14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: Pass over tools

\header{Dates of competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2019.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.

The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

\header{Tools.} 
The competition uses a number of its own tools/scripts to run the competition. We briefly describe these tools. Unless stated otherwise the tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}. {\color{red} Some tools have not been released yet.}
\begin{itemize}
	\item \textbf{Benchmark Selection.} This script implements the benchmark selection policy described on page~\pageref{benchmark-selection}. It takes a seed for the random benchmark selection. The same seed is used for all tools requiring randomisation.
	\item \textbf{Scramber.} This tool is used to scramble benchmarks during the competition to ensure that tools do not rely on syntactic features to identify benchmarks. The scramber can be found at \url{https://github.com/SMT-COMP/scrambler}.
	\item \textbf{Trace Executor.} This tool is used in the interactive track to emulate an on-line interaction between an SMT solver and a client application and is available at \url{https://github.com/SMT-COMP/trace-executor}
	\item \textbf{Postprocessors.} These are used by StarExec to translate the output of tools to the format required for scoring. The postprocessors (per track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
	\item \textbf{Scoring.} This script implements the scoring computation described on in Section~\ref{sec:scoring}. It also includes the scoring computations used in previous competitions (since 2015).
\end{itemize}

>>>>

\header{Dates of Competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2019.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.
%
The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

\header{Tools.}
The competition uses a number of tools/scripts to run the competition. In the
following, we briefly describe these tools. Unless stated otherwise, these
tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}.
{\color{red} Some tools have not been released yet.}
\begin{itemize}
  \item \textbf{Benchmark Selection.} We use a script to implement the
    benchmark selection policy described on page~\pageref{benchmark-selection}.
    It takes a seed for the random benchmark selection. The same seed is used
    for all tools requiring randomisation.
  \item \textbf{Scrambler.} This tool is used to scramble benchmarks during the
    competition to ensure that tools do not rely on syntactic features to
    identify benchmarks. The scrambler can be found at
    \url{https://github.com/SMT-COMP/scrambler}.
  \item \textbf{Trace Executor.} This tool is used in the \inctrack to emulate
    an on-line interaction between an SMT solver and a client application and
    is available at \url{https://github.com/SMT-COMP/trace-executor}
  \item \textbf{Postprocessors.} These are used by StarExec to translate the
    output of tools to the format required for scoring. All postprocessors (per
    track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
  \item \textbf{Scoring.} We use a script to implement the scoring computation
    described on in Section~\ref{sec:scoring}. It also includes the scoring
    computations used in previous competitions (since 2015).
\end{itemize}
